---
title: "W_UP_01"
author: "jesus16"
date: "july 25, 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

We are trying to find the average number of push ups between line players and skilled players. is there a statistical difference in the average number of push ups between players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

We will be analyzing the push ups using Num~Cat for the average of players. The method used will be a box plot, numerical summary for the numerical descriptive results. We will also be including a t-test.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

The skill players are doing on average more push ups than the line players.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

The skill players are in mean are doing about 3X more push ups then the line players. The line players on mean are 17.1, this is in a 2 minute time frame.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


  
```{r}
t.test(pushups~position,data=mydata)
```

After the t-test the P-value= .000009421. Since there is a difference in the amount of push ups the skill players and line players can do. After the looking at the t-test, we reject the null hypothesis.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question is; there is no difference between the average number of pushups of line vs skill players. Based on the data provided, we can conclude that we reject the null, there is a significant differnce on the amount of push ups the skill players and line players.


